%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A clean template for an academic CV
%
% Uses tabularx to create two column entries (date and job/edu/citation).
% Defines commands to make adding entries simpler.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}

% Full Unicode support for non-ASCII characters
\usepackage[utf8]{inputenc}

% Useful aliases
\newcommand{\UERJ}{Universidade do Estado do Rio de Janeiro}
\newcommand{\UHM}{University of Hawai`i at M\={a}noa}
\newcommand{\SOEST}{School of Ocean and Earth Science and Technology}
\newcommand{\UHEARTH}{Department of Earth Sciences}
\newcommand{\LIVEARTH}{Department of Earth, Ocean and Ecological Sciences}
\newcommand{\LIVENV}{School of Environmental Sciences}
\newcommand{\LIV}{University of Liverpool}
\newcommand{\DP}{Department of Physiology}
\newcommand{\FM}{Faculty of Medicine}
\newcommand{\MU}{McGill University}

% Identifying information
\newcommand{\Title}{Curriculum Vit\ae}
\newcommand{\FirstName}{Thomas M.}
\newcommand{\LastName}{Bury}
\newcommand{\Initials}{T. M}
\newcommand{\MyName}{\FirstName\ \LastName}
\newcommand{\Me}{\textbf{T. M. Bury}}  % For citations
\newcommand{\Email}{thomas.bury@mcgill.ca}
\newcommand{\PersonalWebsite}{thomas-bury.research.mcgill.ca}
\newcommand{\LabWebsite}{compgeolab.org}
\newcommand{\ORCID}{0000-0003-1595-9444}
\newcommand{\Affiliation}{\DP \\ \FM \\ \MU}
\newcommand{\Address}{
  Montréal, QC\\ H3A 0G4 Canada
}

% Names for citing coauthors
\newcommand{\Val}{Barbosa, VCF}
\newcommand{\Bi}{Oliveira Jr, VC}
\newcommand{\Paul}{Wessel, P}
\newcommand{\Joaquim}{Luis, J}
\newcommand{\Remko}{Scharroo, R}
\newcommand{\Florian}{Wobbe, F}
\newcommand{\Walter}{Smith, WHF}
\newcommand{\Dongdong}{Tian, D}
\newcommand{\Bridget}{Smith-Konter, B}
\newcommand{\Eric}{Xu, X}
\newcommand{\David}{Sandwell, DT}
\newcommand{\Carla}{Braitenberg, C}
\newcommand{\Naomi}{Ussami, N}
\newcommand{\Manoel}{D'Agrella-Filho, MS}
\newcommand{\JB}{Silva, JBC}
\newcommand{\Dai}{Sales, DP}
\newcommand{\Figura}{Melo, FF}
\newcommand{\Dio}{Carlos, DU}
\newcommand{\BragaVale}{Braga, MA}
\newcommand{\YLi}{Li, Y}
\newcommand{\Angeli}{Angeli, G}
\newcommand{\Peres}{Peres, G}
\newcommand{\Everton}{Bomfim, EP}
\newcommand{\Eder}{Molina, E}
\newcommand{\Gomes}{Gomes, AAS}
\newcommand{\Santiago}{Soler, SR}
\newcommand{\Agustina}{Pesce, A}
\newcommand{\Gimenez}{Gimenez, ME}
\newcommand{\Kristoffer}{Hallam, KAT}
\newcommand{\Guangdong}{Zhao, G}
\newcommand{\Bo}{Chen, B}
\newcommand{\JLiu}{Liu, J}
\newcommand{\LChen}{Chen, L}
\newcommand{\RGuo}{Guo, R}
\newcommand{\MKaban}{Kaban, MK}
\newcommand{\Lindsey}{Heagy, LJ}
\newcommand{\Lion}{Krischer, L}
\newcommand{\Rene}{Gassmoeller, R}
\newcommand{\Bane}{Sullivan, CB}
\newcommand{\Jens}{Klump, JF}
\newcommand{\LBarba}{Barba, LA}
\newcommand{\JBazan}{Bazan, J}
\newcommand{\JBrown}{Brown, J}
\newcommand{\RGuimera}{Guimera, RV}
\newcommand{\MGymrek}{Gymrek, M}
\newcommand{\AHanna}{Alex Hanna}
\newcommand{\KHuff}{Huff, KD}
\newcommand{\DKatz}{Katz, DS}
\newcommand{\CMadan}{Madan, CR}
\newcommand{\KMoerman}{Moerman, KM}
\newcommand{\KNiemeyer}{Niemeyer, KE}
\newcommand{\JPoulson}{Poulson, JL}
\newcommand{\PPrins}{Prins, P}
\newcommand{\KRam}{Ram, K}
\newcommand{\ARokem}{Rokem, A}
\newcommand{\Arfon}{Smith, AM}
\newcommand{\GThiruvathukal}{Thiruvathukal, GK}
\newcommand{\KThyng}{Thyng, KM}
\newcommand{\BWilson}{Wilson, BE}
\newcommand{\Yehudi}{Yehudi, Y}
\newcommand{\Remi}{Rampin, R}
\newcommand{\Hugo}{van Kemenade, H}
\newcommand{\MattTurk}{Turk, M}
\newcommand{\Shapero}{Shapero, D}
\newcommand{\Anderson}{Banihirwe, A}
\newcommand{\Leeman}{Leeman, J}
\newcommand{\JEbbing}{Ebbing, J}
\newcommand{\AGuy}{Guy, A}
\newcommand{\JFarquharson}{Farquharson, J}
\newcommand{\AKushnir}{Kushnir, A}
\newcommand{\FWadsworth}{Wadsworth, F}
\newcommand{\LPerozzi}{Perozzi, L}
\newcommand{\MWieczorek}{Wieczorek, MA}


% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% Icon fonts (requires using xelatex or luatex)
\usepackage[fixed]{fontawesome5}
\usepackage{academicons}

% Template variables for styling
\newcommand{\TablePad}{\vspace{-0.4cm}}
\newcommand{\SoftwareTitle}[1]{{\bfseries #1}}
\newcommand{\TableTitle}[1]{{\fontsize{12pt}{0}\selectfont \itshape #1}}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.12\textwidth}@{\hspace{0.02\textwidth}}p{0.86\textwidth}@{}}
  \BODY
\end{tabularx}
}

% Macros to add links and mark publications
\newcommand{\DOI}[1]{doi:\href{https://doi.org/#1}{#1}}
\newcommand{\DOILink}[1]{\href{https://doi.org/#1}{doi.org/#1}}
\newcommand{\Preprint}[1]{\newline • Preprint: \faFilePdf\ \DOILink{#1}}
%\newcommand{\Media}[1]{\newline • Article: \faFilePdf\ }
\newcommand{\Youtube}[1]{\newline • Recording: \faYoutube\, \href{https://www.youtube.com/watch?v=#1}{youtube.com/watch?v=#1}}
\newcommand{\RecordingDrive}[1]{\newline • Recording: \faGoogleDrive\, \href{https://drive.google.com/file/d/#1/view}{drive.google.com/file/d/#1}}
\newcommand{\GitHub}[1]{\newline • Code: \faGithub\ \href{https://github.com/#1}{#1}}
\newcommand{\Role}[1]{\newline • Role: #1}
\newcommand{\Website}[1]{\newline • Website: \href{https://#1}{#1}}
\newcommand{\Slides}[1]{\newline • Slides: \faTv\ \href{https://#1}{#1}}
\newcommand{\SlidesDOI}[1]{\newline • Slides: \faTv\ \DOILink{#1}}
\newcommand{\PosterDOI}[1]{\newline • Poster: \faImage\ \DOILink{#1}}
\newcommand{\OA}{\aiOpenAccess\enspace}
\newcommand{\Invited}{\newline • \textbf{Invited talk}}

% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{10pt}{0}\selectfont #1 -- #2}
\newcommand{\Year}[1]{\fontsize{10pt}{0}\selectfont #1}
\newcommand{\Ongoing}{present}
%\newcommand{\Ongoing}{$\ast$}
\newcommand{\Future}{future}
\newcommand{\Review}{in review}
\newcommand{\Accepted}{accepted}
\newcommand{\Appointment}[4]{\textbf{#1} \newline #2 \newline #3 \newline #4}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[a4paper,margin=1.5cm,includehead,headsep=5mm]{geometry}

% To get the total page numbers (\pageref{LastPage})
\usepackage{lastpage}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.5}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{nosep}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts. Requires compilation with xelatex
\usepackage{fontspec}  % required to make older xelatex compile with UTF8

% Configure the font style for sections
\usepackage{sectsty}
\sectionfont{\vspace{0.5cm}\bfseries\fontsize{12pt}{0}\selectfont\uppercase}
\subsectionfont{\vspace{0.2cm}\mdseries\fontsize{12pt}{0}\selectfont\uppercase}

% Set the spacing for sections
%\usepackage{titlesec}
%\titlespacing{\section}{0pt}{0cm}{0.3cm}
%\titlespacing{\subsection}{0pt}{0.3cm}{0.3cm}

% Disable number of sections. Use this instead of "section*" so that the sections still
% appear as PDF bookmarks. Otherwise, would have to add the table of contents entries
% manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\chead{
  \fontsize{10pt}{12pt}\selectfont
  \MyName
  \hspace{0.2cm} -- \hspace{0.2cm}
  \Title
  \hspace{0.2cm} -- \hspace{0.2cm}
  \monthyear\today
}
\rhead{\fontsize{10pt}{0}\selectfont \thepage/\pageref*{LastPage}}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
  pdftitle={\MyName\ - \Title},
  pdfauthor={\MyName},
  linkcolor=blue,
  citecolor=blue,
  filecolor=black,
  urlcolor=MidnightBlue
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% No header for the first page
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HEADER
{\fontsize{22pt}{0}\selectfont\MyName}\\[-0.1cm]
\rule{\textwidth}{0.2pt}
\begin{minipage}[t]{0.595\textwidth}
  \Affiliation
  \\
  \Address
\end{minipage}
\begin{minipage}[t]{0.405\textwidth}
  \begin{flushright}
  Last updated: \monthyear\today
  \\
    ORCID: \href{https://orcid.org/\ORCID}{\ORCID}
    \\
    Email: \href{mailto:\Email}{\Email}
%    \\
%    Research group: \href{https://www.\LabWebsite}{\LabWebsite}
    \\
    Website: \href{http://\PersonalWebsite}{\PersonalWebsite}
    \\
    Google Scholar: \href{https://scholar.google.ca/citations?user=qAp4KBYAAAAJ&hl=en&oi=ao}{scholar.google.ca}
  \end{flushright}
\end{minipage}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\begin{EntriesTable}
  \Duration{2015}{2019}  &
  \textbf{PhD, Applied Mathematics}, University of Waterloo, Canada
  \newline
  Thesis: Detecting and distinguishing transitions in ecological systems: model and data-driven approaches.
  \newline
  GPA: 96.4\%
  \newline
  Advisors: Dr. Chris Bauch, Dr. Madhur Anand
  \\
  \Duration{2014}{2015}  &
  \textbf{MMATH, Mathematics}, University of Cambridge, UK
  \newline
  First class honours.\newline
  Director of studies: Dr. Julia Gog, OBE
  \\
  \Duration{2011}{2014}  &
  \textbf{BSc, Mathematics}, University of Cambridge, UK
\end{EntriesTable}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional Appointments}

\begin{EntriesTable}
  \Duration{2020}{\Ongoing}  &
  \Appointment{Postdoctoral Researcher}{\DP}{\FM}{\MU, Canada}
  \\
\end{EntriesTable}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Grants \& Fellowships}
\section{Fellowships}

\begin{EntriesTable}
  \Duration{2021}{2022}  &
  CAMBAM postdoctoral fellowship, Centre for Applied Mathematics in Bioscience and Medicine, McGill University (\$10,000)
  \\
  \Duration{2020}{2021}  &
  CAMBAM postdoctoral fellowship, Centre for Applied Mathematics in Bioscience and Medicine, McGill University (\$7,000)
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards \& Honors}

\begin{EntriesTable}
  \Year{2019}  &
  Doctoral thesis award, University of Waterloo (\$5000)
  \\
  \Year{2019}  &
  Combined travel grants, Waterloo Institute for Complexity and Innovation (\$2500)
  \\
  \Year{2017}  &
  Research dissemination award, GRADTalks, University of Waterloo (\$500)
  \\
  \Year{2017}  &
  Public speaking award, 2nd place at Fields Thesis Competition, Fields Institute, Toronto (\$300)
  \\
  \Year{2017}  &
  Public speaking award, Finalist at 3MT competition, University of Waterloo (\$100)
  \Youtube{UQ1nW9PNil8}
  

\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}

%\subsection{Preprints}
%
%\begin{EntriesTable}
%\Year{2019}  &
%  \OA
%  \LBarba, \JBazan, \JBrown, \RGuimera, \MGymrek, \AHanna, \Lindsey, \KHuff, \DKatz,
%  \CMadan, \KMoerman, \KNiemeyer, \JPoulson, \PPrins, \KRam, \ARokem, \Arfon,
%  \GThiruvathukal, \KThyng, \Me, \BWilson, \Yehudi.
%  Giving software its due through community-driven review and publication.
%  \emph{OSF Preprints}.
%  \DOI{10.31219/osf.io/f4vx6}
%\end{EntriesTable}


\subsection{Papers}

\begin{EntriesTable}
\Year{2021}  &
  \OA
  \Me, R. Sujith, I. Pavithran, M. Scheffer, T. Lenton, M. Anand, and C. Bauch.
  Deep learning for early warning signals of tipping points.
  \emph{Proceedings of the National Academy of Sciences}.
  \DOI{10.1073/pnas.2106140118}.
  \GitHub{ThomasMBury/deep-early-warnings-pnas}
  \\
  ~ &
  \OA
  J. Menard, \Me, C. T. Bauch, and M. Anand.
  When conflicts get heated, so does the planet: coupled social-climate dynamics under inequality
  \emph{Proceedings of the Royal Society B}.
  \DOI{10.1098/rspb.2021.1357}.
  \GitHub{HerdOfBears/Sociodynamics}
  \\
\Year{2020}  &
  \Me, C. Lerma, G. Bub, Z. Laksman, M. W. Deyell, L. Glass.
  Long ECGs reveal rich and robust dynamical regimes in patients with frequent ectopy.
  \emph{Chaos}.
  \DOI{10.1063/5.0023987}.
  \\
  ~ &
  \OA
  \Me, C. T. Bauch, M. Anand.
  Detecting and distinguishing tipping points using spectral early warning signals.
  \emph{Journal of the Royal Society Interface}.
  \DOI{10.1098/rsif.2020.0482}.
  \GitHub{ThomasMBury/ewstools}
  \\
\Year{2019}  &
  \OA
  \Me, C. T. Bauch, M. Anand.
  Charting pathways to climate change mitigation in a coupled socio-climate model.
  \emph{PLoS computational biology}.
  \DOI{10.1371/journal.pcbi.1007000}.
  \GitHub{ThomasMBury/socio\_climate\_model}
 \\
  ~ &
  \OA
  D. A. Pananos, \Me, C. Wang, J. Schonfeld, S. P. Mohanty, B. Nyhan, M. Salathé, C. T. Bauch.
  Critical dynamics in population vaccinating behavior.
  \emph{Proceedings of the National Academy of Sciences}
  \DOI{10.1073/pnas.1704093114}.
\end{EntriesTable}

%
%\subsection{Conference proceedings (peer-reviewed)}

%
%\subsection{Open Datasets}



\subsection{Open-source Software}

\begin{EntriesTable}
  \Duration{2019}{\Ongoing} &
  \textbf{ewstools}
  \newline
  A Python package for computing early warning signals for bifurcations in time series data.
  \DOI{10.5281/zenodo.3497512}
  \Role{Creator, core developer}
  \GitHub{ThomasMBury/ewstools}
%  \Website{www.pygmt.org}
\end{EntriesTable}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Presentations}

\begin{EntriesTable}

\Year{2021} &
  \Me, R. Sujith, I. Pavithran, M. Scheffer, T. Lenton, M. Anand, and C. Bauch.
  Deep learning for early warning signals of bifurcations.
  \emph{Dynamics Days Europe},
  Virtual.
  \SlidesDOI{10.6084/m9.figshare.16892431.v1}
  \\
  ~ &
  \Me, C. Lerma, G. Bub, Z. Laksman, M. W. Deyell, L. Glass.
  Long ECGs reveal rich and robust dynamical regimes in patients with frequent PVCs.
  \emph{Society for Mathematical Biology Annual Meeting},
  Virtual.
  \SlidesDOI{10.6084/m9.figshare.16892593.v1}  
  \\
  ~ &
  \Me, C. Lerma, G. Bub, Z. Laksman, M. W. Deyell, L. Glass.
  Patterns of premature ventricular complexes in the human heart.
  \emph{Department of Physiology Seminar Series, McGill University},
  Virtual.
  \Invited{}
  \\
\Year{2020} &
  \Me, C. T. Bauch, M. Anand.
  Detecting and distinguishing bifurcations from noisy time series data.
  \emph{Applied Mathematics Seminar, Centre de Recherches Mathématiques},
  Virtual.
  \Invited{}
  \Youtube{QGs2knhnXDM}
  \SlidesDOI{10.6084/m9.figshare.16892632.v1}
  \\
  ~ &
  \Me.
  Bifurcations in the era of big data: Applications to cardiology and ecology.
  \emph{Applied Mathematics Seminar Series, University of Ottawa},
  Virtual.
  \Invited{}
  \\
  ~ &
  \Me.
  Bifurcations in the era of big data: Applications to cardiology and ecology.
  \emph{Seminar Series in Quantitative Life Sciences and Medicine, University of McGill},
  Virtual.
  \Invited{}
  \\
  ~ & 
  \Me, M. Anand, C. T. Bauch.
  Fold or Flip? Distinguishing bifurcations in advance with spectral early warning signals.
  \emph{Workshop on Critical Transitions in Complex Systems, Shanghai Institutes for Biological Sciences},
  Virtual.
  \Invited{}
  \RecordingDrive{1kp2G6q-Eu-H13JpVgUCcbezF\_rZzKjJ3}
  \SlidesDOI{10.6084/m9.figshare.16892644.v1}
  \\
\Year{2019} &
  \Me, C. T. Bauch, M. Anand.
  Spectral early warning signals improve tipping point detection and description.
  \emph{Society for Mathematical Biology Annual Meeting},
  Montréal, Canada.
  \PosterDOI{10.6084/m9.figshare.16892395.v2}
  \\
  ~ &
  \Me, C. T. Bauch, M. Anand.
  Spectral early warning signals improve tipping point detection and description.
  \emph{Canadian Society of Applied and Industrial Mathematics, Annual Meeting 2019},
  Whistler, Canada.
  \SlidesDOI{10.6084/m9.figshare.16892662.v1}
  \\
\Year{2018} &
  \Me, M. Anand, C. T. Bauch.
  Early warning indicators of ecological tipping points. Do they predict critical transitions, or something else?
  \emph{Ecological Society of America, Annual Meeting},
  New Orleans, U.S.
  \Invited{}
  \\
  ~ &
  \Me, M. Anand, C. T. Bauch.
  Characterizing impending transitions in complex systems.
  \emph{Dynamics Days US 2018},
  Denver, U.S.
  \\  
\Year{2017} &
  \Me.
  The mathematics of tipping points.
  \emph{TEDx, University of Toronto},
  Toronto, Canada.
  \Invited{}
  \Youtube{pfm7OqBVA6I}
  \\
  ~ &
  \Me, M. Anand, C. T. Bauch.
  Anticipating Critical Transitions in Socio-Ecological Systems
  \emph{Applied Mathematics, Modeling and Computational Science, International Conference},
  Waterloo, Canada.
  \\
  ~ &
  \Me, M. Anand, C. T. Bauch.
  Regime Shifts in Socio-Ecological Systems
  \emph{Mathematical Models in Ecology and Evolution, Conference},
  London, UK.
  \\
  ~ &
  \Me, M. Anand, C. T. Bauch.
  Regime Shifts in Socio-Ecological Systems
  \emph{Waterloo Institute for Complexity and Innovation, Interdisciplinary Conference on Resilience in Complex Natural and Human Systems},
  Waterloo, Canada. 
  \\
\end{EntriesTable}





\section{Media Coverage (selected)}
My research has been broadcast by over 40 different national and international news outlets.

\begin{EntriesTable}
 \Year{2021} &
 The Independent\newline
 • \faNewspaper[regular] \href{https://www.independent.co.uk/climate-change/news/climate-tipping-points-artificial-intelligence-b1925735.html}{independent.co.uk/climate-change/news/}
\\

 \Year{2021} &
 The Daily Mail\newline
 • \faNewspaper[regular] \href{https://www.dailymail.co.uk/sciencetech/article-10021757/Artificial-intelligence-reveal-climate-changes-tipping-points-act-like-early-warning-system.html}{dailymail.co.uk/sciencetech/}
\\
 \Year{2019} &
 Canadian Broadcasting Corporation\newline
 • \faNewspaper[regular] \href{https://www.cbc.ca/news/canada/kitchener-waterloo/guelph-environment-1.5170572}{cbc.ca/news/canada/}
\\
 \Year{2019} &
 The Indian Express\newline
 • \faNewspaper[regular] \href{https://indianexpress.com/article/lifestyle/life-style/social-interactions-can-help-slow-climate-change-study-5773829/}{indianexpress.com/article/}
\\
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching}

\subsection{Graduate}

\begin{EntriesTable}
  \Year{2021} &
  \textbf{Instructor}, \textit{McGill University} \newline 
%  QLSC 600D1: 
  Foundations of Quantitative Life Sciences, 
  (Fall 2021)
%  \newline
%  • 14 graduate students, 1 teaching assistant. \newline
%  • Co-instructed module on `Resetting and Entraining Biological Oscillators'.\newline
%  • Designed project and class material
  \\

  \Duration{2017}{2018} &
  \textbf{Teaching Assistant and Guest Lecturer}, \textit{University of Waterloo} \newline
%  AMATH 777 - 
  Stochastic Processes in the Physical Sciences, 
  (Winter 2017, Winter 2018)
%  \newline
%  • 15-20 graduate students, 1 teaching assistant. \newline
%  • Guest lectured, extended course notes, marked assignments.
  \\
  
  \Year{2017} &
  \textbf{Teaching Assistant}, \textit{University of Waterloo} \newline
  Mathematical Modeling with Differential Equations, 
  (Fall 2017)
  \\
  \end{EntriesTable}



\subsection{Undergraduate}

\begin{EntriesTable}
  \Year{2018} &
  \textbf{Instructor}, \textit{University of Waterloo} \newline 
%  MATH 127: 
  Calculus I for the Sciences, 
  (Fall 2018)
%  \newline
%  • 115 undergraduate students, 1 teaching assistant. \newline
%  • Designed and implemented 36 one-hour lectures with elements of active learning.\newline
%  • Strong student evaluations: mean rating >4.5/5 for each teaching aspect surveyed.
  \\
  \Year{2018} &
  \textbf{Teaching Assistant}, \textit{University of Waterloo}\newline
  Partial Differential Equations I
  (Winter 2018)
  \\
  \Year{2016} &
  \textbf{Teaching Assistant}, \textit{University of Waterloo}\newline
  Introduction to Differential Equations,
  (Winter 2016)
  \\
  \Duration{2015}{2016} &
  \textbf{Teaching Assistant}, \textit{University of Waterloo}\newline
%   MATH 117 - 
   Various calculus courses for math and engineering students\newline 
   (Fall 2015, Summer 2016, Fall 2016)
%   \newline
%  • 667 undergraduate students, 11 teaching assistants. \newline
%  • Designed weekly problem sheets and solutions for the entire course.\newline
%  • Ran interactive tutorial sessions, held office hours, marked and proctored exams.
  \\
  

\end{EntriesTable}






\subsection{Credentials}

\begin{EntriesTable}
\Duration{2017}{2019} &
  Certificate of University Teaching, \textit{University of Waterloo}\newline
  An in-depth, selective, 2-year teaching course for PhD students. 
  Includes multiple teaching observations, guided self-reflection and improvement, workshops and a pedagogical research project.
  \\
\Duration{2015}{2016}  &
  Fundamentals of University Teaching, \textit{University of Waterloo}\newline
  Includes weekly workshops on teaching fundamentals including active learning, equitable teaching, and effective delivery.
\end{EntriesTable}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Student supervision}

\subsection{P\lowercase{h}D}

\begin{EntriesTable}
\Duration{2019}{\Ongoing}  &
  Khady Diagne (co-advisor)\newline
  McGill University\newline
  Project: Spatio-temporal dynamics of pure parasystole in cardiac tissue
\end{EntriesTable}


%\subsection{Masters}
%
%\begin{EntriesTable}
%\Duration{2019}{\Ongoing}  &
%  Jyler Menard (mentor)\newline
%  University of Waterloo\newline
%\end{EntriesTable}
%

\subsection{Undergraduate}

\begin{EntriesTable}
\Duration{2020}{2021}  &
  Alix Vanpoperinghe (advisor)\newline
  McGill University\newline
  Project: Simulation of cardiac monolayers under optogenetic control
  \GitHub{alixvanpo/opto-project}
  \\
\Duration{2020}{2021}  &
  Glisant Plasa (co-advisor)\newline
  McGill University\newline
  Project: Reinforcement learning for discovery of reentry mechanisms in cardiac tissue
\end{EntriesTable}


%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Outreach}
%
%I maintain a blog about my research, geoscience, and programming at
%\href{https://www.leouieda.com/blog}{leouieda.com/blog}
%\\
%
%\begin{EntriesTable}
%\Year{2018}  &
%  Interviewed by the geoscience podcast \textit{Don't Panic Geocast}, episode 166
%  \textit{``You are headed to a warm and sunny place''}:
%  \href{http://www.dontpanicgeocast.com/?p=638}{dontpanicgeocast.com/?p=638}
%  \\
%\Year{2017}  &
%  Volunteer for the \textit{Hour of Code} at Salt Lake Elementary School, Honolulu,
%  USA.
%  \\
%\Year{2016}  &
%  Interviewed by the geoscience podcast \textit{Undersampled Radio}, episode
%  \textit{``Open Sourcery''}:
%  \href{https://undersampledrad.io/home/2016/7/open-sourcery}{undersampledrad.io/home/2016/7/open-sourcery}
%\end{EntriesTable}
%
%Geophysical tutorials for the SEG publication \textit{The Leading Edge}:
%\\
%
%\begin{EntriesTable}
%\Year{2017}  &
%  \OA
%  \Me.
%  Step-by-step NMO correction,
%  \emph{The Leading Edge},
%  \DOI{10.1190/tle36020179.1}.
%  \GitHub{pinga-lab/nmo-tutorial}
%  \\
%\Year{2014}  &
%  \OA
%  \Me, \Bi, \Val.
%  Geophysical tutorial: Euler deconvolution of potential-field data,
%  \emph{The Leading Edge},
%  \DOI{10.1190/tle33040448.1}.
%  \GitHub{pinga-lab/paper-tle-euler-tutorial}
%\end{EntriesTable}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Academic Service}
%
%\subsection{Editor}
%
%\begin{EntriesTable}
%  \Duration{2019}{\Ongoing} & Topic editor for the \textit{Journal of Open Source Software}
%\end{EntriesTable}
%
%\subsection{Community service}
%
%\begin{EntriesTable}
%  \Duration{2019}{\Ongoing} & EarthArXiv Advisory Council
%\end{EntriesTable}

\subsection{Committees}

\begin{EntriesTable}

\Year{2021} &
  CGSM evaluation committee member, \emph{McGill University}\newline
  Served as an evaluator for the 2021-2022 Canada Graduate Scholarship-Master’s competition.
  \\

\Duration{2017}{2018} &
  Senate Graduate and Research Council, \emph{University of Waterloo}\newline
  Served as the math grad student representative for matters of academic quality and research activity within the university.
  \\
\end{EntriesTable}


\subsection{Summer schools and workshops}
\begin{EntriesTable}
  \Year{2021} & 
  Summer School in Nonlinear Dynamics for the Life Sciences (online)\newline
  \emph{CAMBAM and NSERC-CREATE, McGill University}\newline
  Technical lead for 2-week, international summer school with 50 participants and 24 instructors.
  \\

\Year{2020} &
  Interactive Data Visualisation in Python (online)\newline
  \textit{CAMBAM-CRM, McGill University}\newline
  Designed and implemented 5-hour workshop with
%  Involved Jupyter notebooks with exercises and public datasets for participants. 
  60 participants including students and faculty.
  \GitHub{ThomasMBury/workshop\_datavis\_python}
  \\
\Year{2018}  &
  A Hands-on Introduction to Mathematical Modelling\newline
  \textit{Waterloo Institute for Complexity and Innovation: Leveraging systems approaches to improve human and planetary health}\newline
  Co-designed and implemented 4-hour workshop.
  %that explores mathematical modelling with differential equations and agent-based models in the context of human and planetary health.

  
\end{EntriesTable}





\subsection{Outreach}
\begin{EntriesTable}
  \Year{2021} &
  Interviews with media outlets including \emph{The Scientific American}, \emph{The Waterloo Region Record}, \emph{The McGill Tribune} and \emph{The Charlatan}.
  \\
  \Duration{2016}{2018} & 
  Workshop facilitator at primary school visits. \emph{Let's Talk Science}, Waterloo, Canada.
  \\
%  Let’s Talk Science: National, charitable organisation for STEM outreach across schools in Canada. 
%  Volunteered on school visits to demonstrate physics concepts to children in Grades 4-6.
%  \\
  \Year{2017} & 
  TEDx speaker. \emph{University of Toronto}, Toronto, Canada.
  \\
  ~ &
  GRADTalks speaker and panelist \emph{University of Waterloo}, Waterloo, Canada.
\\
  ~ & 
  Volunteer at Physics Lab Day for Grade 11-12. \emph{University of Waterloo}, Waterloo, Canada.
\\
  ~ & 
  Science fair judge for Grade 8 projects. \emph{Centennial Public School}, Waterloo, Canada.
\end{EntriesTable}



%\subsection{Conference Convener}

\subsection{Reviewer}

\begin{itemize}
  \item Physics Review X
  \item Ecology Letters
  \item Proceedings of the Royal Society A
  \item Proceedings of the Royal Society B
  \item Journal of the Royal Society Interface
  \item Chaos 
  \item Ecological Economics
  \item Climatic Change
  \item PLOS One

\end{itemize}

%\subsection{Affiliations}





\section{Languages}

\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.15\textwidth} p{0.85\textwidth}@{}}
  English & Native
  \\
  French & TEFaQ Level C1 (proficiency) obtained in 2020.
\end{tabularx}

\end{document}
